Order reduction and MILP models for real-time DNN robustness certification.

### 2025-08-02 AAAI2026/global.tex
polish

    To encode global robustness, \cite{vhagar} considers
	variable $x_j,\hat{x}_j$ and $x'_j,\hat{x}'_j$ for nodes of the image $I$ 
	and of its perturbation $I'$, 
	using the classical encoding (\ref{eq11}) \cite{MILP} 
	to compute $\hat{x}_i, \hat{x}'_i$ from $x_i, x'_i$
	for each $i$.
    Further:
    \begin{enumerate}
		\item For each input nodes $x_j,x'_j$ of $I,I'$, add constraints
        $|x_j-x'_j| \leq \varepsilon$ 
        ($L_\infty$-perturbation - see later for $L_1$).
		\item The optimization objective is to maximize $x_C - x_D +x'_D - x'_C$ 
		to compute $\beta^\varepsilon_{C,D}=\beta^\varepsilon_{D,C}$, 
		for $C \neq D$ two decision classes.
	\end{enumerate}

>>>>

    To encode global robustness, \cite{vhagar} considers
	variable $x_j,\hat{x}_j$ and $x'_j,\hat{x}'_j$ for nodes of the image $I$ 
	and of its perturbation $I'$, 
	using the classical encoding (\ref{eq11}) \cite{MILP} 
	to compute $\hat{x}_i, \hat{x}'_i$ from $x_i, x'_i$
	for each $i$.
    Further:
    \begin{enumerate}
		\item For each input nodes $x_j,x'_j$ of $I,I'$, add constraints
        $|x_j-x'_j| \leq \varepsilon$ 
        ($L_\infty$-perturbation - see later for $L_1$).
		\item The optimization objective is to maximize $x_C - x_D +x'_D - x'_C$ 
		to compute $\beta^\varepsilon_{C,D}=\beta^\varepsilon_{D,C}$, 
		for $C \neq D$  decision classes, as proposed in \cite{vhagar}.
	\end{enumerate}
